%\subsection{\nexp\ Strategy}

Precision frontier experiments require very high statistics as well as extensive evaluation of systematic uncertainties, backgrounds, biases and distortions in the data selection criteria. The two most recent pion decay experiments, TRIUMF PIENU and PSI PEN  provide highly insightful information on the  limitations of their techniques and the principal systematic effects which we have incorporated into our design concepts discussed below. These  measurements were performed using stopped pions that decay at rest either directly to a positron and a neutrino ($\pi^+ \rightarrow e^+ \nu$ decay) or first to a muon (and associated neutrino) that subsequently undergoes 3-body decay at rest in the target (decay chain $\pi^+ \rightarrow \mu^+ \rightarrow e^+$).  The  energy and time characteristics of the positrons emerging from those two decays are very different, and thus can be used to distinguish the decay channels. By measuring the ratio of positrons detected from the two channels, many systematic effects (e.g. pion counting, solid angle acceptance, efficiency, etc.) cancel out to first order, aiding in reaching high precision.  Despite being  mono-energetic the positrons originating from $\pi^+ \rightarrow e^+ \nu$ decays have their energy distribution broadened due to finite energy resolution of the calorimeter, shower leakages of low energy photons from the sides and ends of the calorimeter as well as the presence of radiative decays. Those effects result in a low energy tail hidden under the Michel spectrum and lead to the main correction and largest source of systematic effects in the branching ratio measurement. In order to minimize the energy tail for a precise experiment, a high resolution,  high radiation-length, and high acceptance calorimeter must be chosen.  Other significant systematic effects are associated with pulse pile-up and decays-in-flight of pions prior to stopping in the target. To supress all these  small effects to the level $< 0.01\%$ we propose to use a highly segmented stopping target.

The new measurement of $R_{e/\mu}$ would build on the techniques refined in the previous
experiments with high energy resolution like TRIUMF PIENU and high acceptance for positrons and
gammas like PSI PEN. In addition, it would employ emerging technologies in 
highly granular 4-dimensional tracking in an active stopping target using low gain avalanche 
diode (LGAD) silicon detectors. The combination of these two features, tracking in a highly
segmented fast active target (ATAR) and a high acceptance fast electromagnetic calorimeter (CALO) promise
to reduce the systematic impact of key challenges in the earlier experiments.

In the following we focus on the $R_{e/\mu}$ aspect of the proposed program because the systematic
requirements for achieving O$(10^{-4})$ precision are very demanding. The pion beta decay experiment
would equally benefit from the fast response of both active target and calorimeter, but the 
target thickness will be increased to spread out the wider stopping range of the 
%foreseen $\sim$100 MeV/c
pion beam with 100-fold higher rate than required for the $\pi \rightarrow e(\mu)$ measurement. 


%\subsection{Statistics}

%It is estimated that $3 \times 10^8\; \pi^+ \rightarrow e^+ \nu$ %events can be collected in two years of operation, satisfying the %statistics goal. 

%In addition to improvements in the precision of the PIENU branching ratio, orders of magnitude improvements would be anticipated in sensitivity to sterile neutrinos in decays $\pi^+ \rightarrow e^+/\mu^+ \nu_H$ and to decays involving dark sector particles like $\pi^+ \rightarrow e^+/\mu^+ \nu \textrm{X}$ as mentioned in Sec. \ref{Exotics}.

%\todo{Statement for PiBeta}


\input{sections/Detector/target}


\input{sections/Detector/calo.tex}

\subsection{Tracking}
\input {sections/Detector/tracking.tex}
\subsection{DAQ}
\input {sections/Detector/daq.tex}
\subsection{Simulations}
\input {sections/Detector/simulations.tex}